---
title: "Hello and welcome to **me, myself, and R**"
author: "by *cocoyamo*"
date: "updated: 2024-06-06"
output:
  html_document: 
    fig_caption: yes
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## introduction

**I have a toxic relationship with R Studio**

Hi, I am a student (not anymore very soon) who has been struggling with R Studio. Loving it and hating it (sometimes).

I use statistical analysis like t-tests, ANOVAs, and linear regressions often. I love to make graphs inside R Studio. Therefore I think it would be a great idea to post my journey here, mostly so that I won't have to go to my past files and copy my codes whenever I want to do a new analysis.

Sometimes I use R Studio to do funny stuff, like drawing national flags, just for fun. So you will probably see those here.

Feel free to leave comments or suggestions, I am still an infant in the fascinating world of R, and am open to learn new things!

Best, *cocoyamo*

Reykjavik, 2024

## first thing first: `install` and `library`

I wish someone use this analogy when I was learning R Studio for the very first time.

People are constantly saying "oh you need to **install** this package", and therefore I install every packages every time I am using R Studio.

Then people will ask you to "call the package out" using a function called `library`.

These two things inside R Studio confused me a lot in the beginning, (and I was mocked by a teaching assistant who was very inconsiderate of people who have never learned coding before), hopefully here you can find some answer. And I will not mock you. I swear. I know the struggles.

I now think of this as making a sandwich. Pick whatever sandwich you like. I will do a peanut butter and chocolate sandwich here.

So, imagine you are going to make peanut butter and chocolate sandwich. You need ingredients. So you went to a nearby grocery store to purchase *chocolate spread*, *peanut butter*, and *toast*. (Feel free to switch to any other food you like, also please do not follow my recipe if you are allergic to peanut!)

This step (getting ingredients from a store) is called `install`.

Then, you go back to your kitchen, pull these ingredients out from your reusable bag, this action is similar to the `library` function.

Let's assume these ingredients will never run out. (What a heaven!) Then, the next time you want the peanut butter and chocolate sandwich, all you need to do is to pull out these ingredients again. **There is no need to go back to the store every time you want it, you already have it in your kitchen!**

Therefore, whenever you need to use some package you have not used before, you need to `install` them first, and then afterwards, the only thing you need to do is to use the `library` function to pull these magical stuff out of your bag.

Okay, I hope you are still with me, and not already in the kitchen looking for your chocolate spread.

## import file/dataset

Let's import our data!

**note: If this is your first time import data, and if your data is from an Excel file, then remember to type `install.packages("readxl")` on your coding space first.**

There are of course tons of ways to import your data, but the following is what I use most often.

I will click `Import Dataset` on the top right corner in the `Environment` box. Then choose `import`, chose `From Excel` (or `From Text` if I have a .csv file), then use `Browse` on the top right corner to pick up the file I want to import.

You can either double-click or click it once and then click the "open" at the bottom right.

The middle part is the `Data Preview`, you can see your data here, don't import the wrong file!(I've done that multiple times, especially when I am lazy at giving files proper names :P)

Then, you look at the bottom right corner, there is a section called `Code Preview`.

The code can look something like this. (But not identical! Because (hopefully) we are using different file names.)

```{r}
library(readxl)
wether_math <- read_excel("~/Documents/MMR/example files/wether_math.xlsx") 
View(wether_math)
```

Now you have seen the `Code Preview` section, at the end of it there is a tiny icon looking like a clipboard, you do what? CLICK IT!

**Great Job!!**

Now you have copied the code necessary to import your file, press `Import` at the bottom right.

Go back to the coding section. Paste (`Ctrl + v`/`Command + v`) it on the coding section (the top left section of the interface).

(Let's hope R Studio never change their interface or else I will have to rewrite this part.)

Also, sometimes you can use `head()` to see the first few rows of your data, just to make sure everything went well.

```{r}
head(wether_math)
```

### a small explanation of this data

Let us take a peek at this data, so you will have a better grasp in our future examples. 

```{r}
View(wether_math)
```

This is a made-up data. There are 10 imaginary people participate in this imaginary research. They do math test on both a rainy day and a sunny day. Their scores were recorded. 
Therefore, the first column is the participant number, the second column is the weather (either sunny or rainy), and the third column is their scores. 

## my happy universe with tidyverse

I really love tidyverse It is a game changer. It contains some of my most-used functions, like ``dplyr`` and ``ggplot2``.
But first we need to know what it is. 
**again, if you have not used ``tidyverse`` before, you also need to download the package first. **

```{r }
#install.packages("tidyverse")
#install.packages("dplyr")
```

Great. Let's goooo.

Here, an important function is called *pipe*. It's one of the greatest analogy in this century. Although how the pipe looks "``%>%``" does not look like a real pipe. We will meet this incredible feature in a few minutes.

```{r}
library(dplyr)
```

For example, we want to use some data to draw a bar chart. 


```{r}
library(readxl)
wether_math <- read_excel("~/Documents/MMR/example files/wether_math.xlsx") 
View(wether_math)
```



## t-tests(with graph)

library(ggplot2)

    binded_2122$year = as.factor(binded_2122$year)

    binded_2122 %>%
      ggplot(aes(x = year, y = ceo_compensation)) +
      geom_bar(stat = "summary", position = position_dodge(.9), width = .35, fill = "#BDD5EA") +
      geom_errorbar(stat = "summary", position = position_dodge(.9), width = .12) +
      #facet_wrap(emotion ~ ., scales = "free")+
      theme_classic()


    ado_chi_acc_rt %>%
      group_by(Subject,age, Consistency, Operation) %>%
      summarise(acc = mean(Response_ACC)) -> semi
    ado_chi_acc_rt %>%
      group_by(Subject,age, Consistency, Operation) %>%
      summarise(medi_rt = median(Response_RT)) -> semi_rt
    semi %>%
      left_join(semi_rt, by = c("Subject", "age", "Consistency","Operation")) -> all_age

    all_age %>%
      ggplot(aes(x = Operation, y = acc, group = Consistency, fill = Consistency)) +
      geom_bar(stat = "summary", position = position_dodge(.8), width = .8) +
       facet_wrap(age~ ., scales = "free")+
      coord_cartesian(ylim = c(0.5,1.05))+
      geom_errorbar(stat = "summary", position = position_dodge(.8), width = .12) +
      theme_light()

## ANOVAs(also with graphs)

    all_age %>%
     # filter(age == "chi")%>%
    #  filter(Operation == "add") %>%
      group_by(age) %>%
      anova_test(
        dv = acc,
        wid = Subject,
        type = NULL,
       #  between = age,
        # within = operation,
        within = c(Consistency,Operation),
       # within = Consistency, 
        effect.size = "ges", #generalized eta squared
        error = NULL,
        white.adjust = FALSE,
        observed = NULL,
        detailed = F) 

## pivot your data like a pro

    ado_roi %>%
      pivot_longer(!Subject, names_to = "key", values_to = "value") -> ado_long_data
    View(ado_long_data)

    separate(
      ado_long_data,
      col = key,
      into = c('Position', 'Location', 'snn', 'sn_num', 
               'Consistency', 'Operation', 'problemsize',
               'bf', 'n1'),
      sep = "[^[:alnum:]]+",
      remove = TRUE,
      convert = FALSE
    ) -> ado_dt
    View(ado_dt)

## left join right join

    sub_RT %>%
       left_join(sub_acc, by = c("subject")) -> sub_RT_acc

## different kinds of binding

    cbind(ado_dt, ado_roi_neat) -> ado_bind
    View(ado_bind)

## select column & row

## let's draw flags!

```{r}
library(ggplot2)
library(dplyr)

lith <- data.frame(name=c("A","B","C") ,
                   value=c(4,4,4))

lith %>%
  ggplot(aes(x = name, y = value)) +
  geom_bar(stat = "summary", width = 1, fill = c("#BE3A34","#046A38","#FFB81C")) +
  coord_flip()+
  theme_void()
```

```{r}
latv <- data.frame(name=c("A","B","C") ,
                   value=c(4,4,4))

latv %>%
  ggplot(aes(x = name, y = value)) +
  geom_bar(stat = "identity", width = c(1.3, 0.9, 1.3), fill = c("#A4343A","#FFFFFF","#A4343A")) +
  coord_flip()+
  theme_void()
```

```{r}
specie <- c("A","B" ,"C","D","E","F","G","H","I")
condition <- c("a","b","c","d","d","c","d","c","d",
               "e","a","b","c","d","c","d" ,"b","c",
               "d","e","a","b","d","c","d","a" ,"b",
               "c","d","e","a","d","c","d","e", "a" ,
               "b","c","d","e","d" ,"c","d","d","e")
value <- c(6, 0.75, 1, 0.75, 3)
data <- data.frame(specie,condition,value)
ggplot(data, aes(fill=condition, y=value, x=specie)) + 
  geom_bar(position="fill", stat="identity", width = 1)+
  scale_fill_manual(values=c("blue", "white", "red","white","blue")) +
  coord_flip() +
  theme_void()


```
