---
title: "Hello and welcome to **me, myself, and R**"
author: "by *cocoyamo*"
date: "updated: 2024-06-06"
output:
  html_document: 
    fig_caption: yes
    theme: simplex
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

**I have a toxic relationship with R Studio**

Hi, I am a student (not anymore very soon) who has been struggling with R Studio. Loving it and hating it (sometimes).

I use statistical analysis like t-tests, ANOVAs, and linear regressions often. I love to make graphs inside R Studio. Therefore I think it would be a great idea to post my journey here, mostly so that I won't have to go to my past files and copy my codes whenever I want to do a new analysis.

Sometimes I use R Studio to do funny stuff, like drawing national flags, just for fun. So you will probably see those here.

Feel free to leave comments or suggestions, I am still an infant in the fascinating world of R, and am open to learn new things!

Best, *cocoyamo*

Reykjavik, 2024

## RStudio Environment and Installation

*first thing first: `install` and `library`*

I wish someone use this analogy when I was learning R Studio for the very first time.

People are constantly saying "oh you need to **install** this package", and therefore I install every packages every time I am using R Studio.

Then people will ask you to "call the package out" using a function called `library`.

These two things inside R Studio confused me a lot in the beginning, (and I was mocked by a TA who was very inconsiderate of people who have never learned coding before), hopefully here you can find some answer. And I will not mock you. I swear. I know the struggles.

I now think of this as making a sandwich. Pick whatever sandwich you like. I will do a peanut butter and chocolate sandwich here.

So, imagine you are going to make peanut butter and chocolate sandwich. You need ingredients. So you went to a nearby grocery store to purchase *chocolate spread*, *peanut butter*, and *toast*. (Feel free to switch to any other food you like, also please do not follow my recipe if you are allergic to peanut or chocolate!)

This step (getting ingredients from a store) is called `install`.

Then, you go back to your kitchen, pull these ingredients out from your reusable bag, this action is similar to the `library` function.

Let's assume these ingredients will never run out. (What a heaven!) Then, the next time you want the peanut butter and chocolate sandwich, all you need to do is to pull out these ingredients again. **There is no need to go back to the store every time you want it, you already have it in your kitchen!**

Therefore, whenever you need to use some package you have not used before, you need to `install` them first, and then afterwards, the only thing you need to do is to use the `library` function to pull these magical stuff out of your bag.

Okay, I hope you are still with me, and not already in the kitchen looking for your chocolate spread.

## Data Import and Reading
Let's import our data!

### Import Your Data

**note: If this is your first time import data, and if your data is from an Excel file, then remember to type `install.packages("readxl")` on your coding space first.**

```{r}
#install.packages("readxl")
#library(readxl)
```

There are of course tons of ways to import your data, but the following is what I use most often.

I will click `Import Dataset` on the top right corner in the `Environment` box. Then choose `import`, chose `From Excel` (or `From Text` if I have a .csv file), then use `Browse` on the top right corner to pick up the file I want to import.

You can either double-click or click it once and then click the `open` at the bottom right.

The middle part is the `Data Preview`, you can see your data here, don't import the wrong file!(I've done that multiple times, especially when I am lazy at giving files proper names :P)

Then, you look at the bottom right corner, there is a section called `Code Preview`.

The code can look something like this. (But not identical! Because (hopefully) we are using different file names.)

```{r}
library(readxl)
wether_math <- read_excel("~/Documents/MMR/example files/wether_math.xlsx")
View(wether_math)
```

Now you have seen the `Code Preview` section, at the end of it there is a tiny icon looking like a clipboard, you do what? CLICK IT!

**Great Job!!**

Now you have copied the code necessary to import your file, press `Import` at the bottom right.

Go back to the coding section. Paste it (`Ctrl/Command + v`) on the coding section (the top left section of the interface).

(Let's hope R Studio never change their interface or else I will have to rewrite this part.)

Also, sometimes you can use `head()` to see the first few rows of your data, just to make sure everything went well. 

```{r}
head(wether_math)
```

Or you could just type in the data names. 

```{r}
wether_math
```

#### Wether Math Data Explanation

Let us take a peek at this data, so you will have a better grasp in our future examples.

```{r}
wether_math
```

This is a made-up data. There are 10 imaginary people participate in this imaginary research. They do math test on both a rainy day and a sunny day. Their scores were recorded. Therefore, the first column is the participant number, the second column is the weather (either sunny or rainy), and the third column is their scores.

### Dataset packages
#### babynames
There are different data packages inside R. We can access those data by simply install them. For example, we can install a package called `babynames` . 

This package contains baby names in the US from year 1880 to year 2017. 

Let us take a look.

```{r}
#install.packages("babynames")
#library(babynames)
#View(babynames)
```

RStudio creates a separate page for the data when we use `View()` . We can see that there are 5 columns: `year`, `sex`, `name`, `n`, and `prop`.

Wait, what is the `prop`? 

When we encounter questions like this, we can type `?+function/dataset` on the Console area. In this case, we typed `?babynames`. 

Once we hit enter, we can see the Help screen on the right side popped up some information. After reading the explanation of this dataset, we learned that `prop` means `n` divided by all babies of that sex with that name born in that year. 

#### starwars

There are also built-in data inside `dplyr` packages. For example, there is a dataset called `starwars`. 

We can import them with a few lines of codes.

```{r}
#install.packages("dplyr")
#library(dplyr)
```

We just called out the `dplyr` package, where `starwars` dataset was stored in. 

```{r}
#starwars
```

### Ways to Check Data

These functions are commonly used for checking data.

`View()` will open a new page for reading datasets. 

`glimpse()` `head()` `tail()` `dim()` `slice()`

Also, you can check the qualities of datasets. For example, `ncol()` & `nrow()` . Both of them can be found at once when using `dim()`.

## Overview of Tidyverse and Core Functions

I really love tidyverse. It is a game changer. Three packages I use most often in tidyverse are:

1.  `ggplot2`
2.  `dplyr`
3.  `tidyr`

But first we need to know what it is.

`Tidyverse` contains several packages, making data transformation and visualization (and my life) easier. Under the umbrella of `tidyverse`, we will be able to wrangle with data like a pro.

We will delve deeper into the land of `ggplot2` in the future chapter. Here, we focus on `dplyr` and `tidyr` first.

**If you have not use `tidyverse` before, you need to download the package first.**

```{r}
#install.packages("tidyverse")
#install.packages("dplyr")
#install.packages("tidyr")
```

Next, let us not forget to also **call out** our packages, which we use `library()` function for the job.

```{r}
library("tidyverse")
library("dplyr")
library("tidyr")
```

You are all set.

Before we jump into anything, let us meet a funny-looking friend. *The pipe.*

It looks like this:

```{r}
#%>%
```

In my humble opinion, this is one of the greatest analogy in this century. Although the way it looks (`%>%`) does not strike me as a real pipe at all.

Let us use an example to see how it works.

### babynames

`babynames` package is a built-in R package. It contains baby names in the US from year 1880 to year 2017.

```{r}
#install.packages("babynames")
library(babynames)
```

We can take a look at the data.

```{r}
View(babynames)
```

RStudio should have created a separate page for the data. We can see that there are 5 columns: `year`, `sex`, `name`, `n`, and `prop`.

Wait, what are `prop`?

When we encounter questions like this, we can type `?+function/dataset` on the Console area. In this case, we typed `?babynames`.

Once we hit enter, we can see the Help screen on the right side popped up some information. After reading the explanation of this dataset, we learned that `prop` means `n` divided by all babies of that sex with that name born in that year.

Now, let's say we want to know names of babies born in year 2000.

```{r}
babynames %>%
	filter(year == 2000)
```

Here we see all the baby names in 2000!

In the code, I used `%>%` to direct my dataset `babynames` into the next function `filter()`.

Inside the `filter()` function, I told the program I want babies who were born in year 2000. In other words, I filtered out the babies which in the 'year' column, says '2000'.

A good thing about the `%>%` is that you can build one after another. Just like you can direct the water from east to west, then from west to north.

Let's try it out.

```{r}
babynames %>%
	filter(year == 2000) %>%
	filter(sex == "F")
```

Here we put F with a quotation mark because it is a character, instead of a number. We need to specify that so that RStudio can understands us.

Now the data is showing female babies who were both born in year 2000.

We can also acquire this output in another way.

```{r}
babynames %>%
 filter(year == 2000 & sex == "F")
```

Let us do more data transformation in the next chapter.



## Data Cleaning and Transformation

## Data Wrangling and Reshaping

## Statistical Analysis

## Data Visualization

## Efficiency Tips for Data Processing

## Data Export

## Colclusion and Advanced Learning










### 


## my happy universe with tidyverse

I really love tidyverse. It is a game changer. Three packages I use most often in tidyverse are:

1.  `ggplot2`
2.  `dplyr`
3.  `tidyr`

But first we need to know what it is.

`Tidyverse` contains several packages, making data transformation and visualization (and my life) easier. Under the umbrella of `tidyverse`, we will be able to wrangle with data like a pro.

We will delve deeper into the land of `ggplot2` in the future chapter. Here, we focus on `dplyr` and `tidyr` first.

**If you have not use `tidyverse` before, you need to download the package first.**

```{r}
#install.packages("tidyverse")
#install.packages("dplyr")
#install.packages("tidyr")
```

Next, let us not forget to also **call out** our packages, which we use `library()` function for the job.

```{r}
library("tidyverse")
library("dplyr")
library("tidyr")
```

You are all set.

Before we jump into anything, let us meet a funny-looking friend. *The pipe.*

It looks like this:

```{r}
#%>%
```

In my humble opinion, this is one of the greatest analogy in this century. Although the way it looks (`%>%`) does not strike me as a real pipe at all.

Let us use an example to see how it works.

### babynames

`babynames` package is a built-in R package. It contains baby names in the US from year 1880 to year 2017.

```{r}
#install.packages("babynames")
library(babynames)
```

We can take a look at the data.

```{r}
View(babynames)
```

RStudio should have created a separate page for the data. We can see that there are 5 columns: `year`, `sex`, `name`, `n`, and `prop`.

Wait, what are `prop`?

When we encounter questions like this, we can type `?+function/dataset` on the Console area. In this case, we typed `?babynames`.

Once we hit enter, we can see the Help screen on the right side popped up some information. After reading the explanation of this dataset, we learned that `prop` means `n` divided by all babies of that sex with that name born in that year.

Now, let's say we want to know names of babies born in year 2000.

```{r}
babynames %>%
	filter(year == 2000)
```

Here we see all the baby names in 2000!

In the code, I used `%>%` to direct my dataset `babynames` into the next function `filter()`.

Inside the `filter()` function, I told the program I want babies who were born in year 2000. In other words, I filtered out the babies which in the 'year' column, says '2000'.

A good thing about the `%>%` is that you can build one after another. Just like you can direct the water from east to west, then from west to north.

Let's try it out.

```{r}
babynames %>%
	filter(year == 2000) %>%
	filter(sex == "F")
```

Here we put F with a quotation mark because it is a character, instead of a number. We need to specify that so that RStudio can understands us.

Now the data is showing female babies who were both born in year 2000.

We can also acquire this output in another way.

```{r}
babynames %>%
 filter(year == 2000 & sex == "F")
```

Let us do more data transformation in the next chapter.
 
## t-tests(with graph)

library(ggplot2)

    binded_2122$year = as.factor(binded_2122$year)

    binded_2122 %>%
      ggplot(aes(x = year, y = ceo_compensation)) +
      geom_bar(stat = "summary", position = position_dodge(.9), width = .35, fill = "#BDD5EA") +
      geom_errorbar(stat = "summary", position = position_dodge(.9), width = .12) +
      #facet_wrap(emotion ~ ., scales = "free")+
      theme_classic()


    ado_chi_acc_rt %>%
      group_by(Subject,age, Consistency, Operation) %>%
      summarise(acc = mean(Response_ACC)) -> semi
    ado_chi_acc_rt %>%
      group_by(Subject,age, Consistency, Operation) %>%
      summarise(medi_rt = median(Response_RT)) -> semi_rt
    semi %>%
      left_join(semi_rt, by = c("Subject", "age", "Consistency","Operation")) -> all_age

    all_age %>%
      ggplot(aes(x = Operation, y = acc, group = Consistency, fill = Consistency)) +
      geom_bar(stat = "summary", position = position_dodge(.8), width = .8) +
       facet_wrap(age~ ., scales = "free")+
      coord_cartesian(ylim = c(0.5,1.05))+
      geom_errorbar(stat = "summary", position = position_dodge(.8), width = .12) +
      theme_light()

## ANOVAs(also with graphs)

    all_age %>%
     # filter(age == "chi")%>%
    #  filter(Operation == "add") %>%
      group_by(age) %>%
      anova_test(
        dv = acc,
        wid = Subject,
        type = NULL,
       #  between = age,
        # within = operation,
        within = c(Consistency,Operation),
       # within = Consistency, 
        effect.size = "ges", #generalized eta squared
        error = NULL,
        white.adjust = FALSE,
        observed = NULL,
        detailed = F) 

## pivot your data like a pro

    ado_roi %>%
      pivot_longer(!Subject, names_to = "key", values_to = "value") -> ado_long_data
    View(ado_long_data)

    separate(
      ado_long_data,
      col = key,
      into = c('Position', 'Location', 'snn', 'sn_num', 
               'Consistency', 'Operation', 'problemsize',
               'bf', 'n1'),
      sep = "[^[:alnum:]]+",
      remove = TRUE,
      convert = FALSE
    ) -> ado_dt
    View(ado_dt)

## left join right join

    sub_RT %>%
       left_join(sub_acc, by = c("subject")) -> sub_RT_acc

## different kinds of binding

    cbind(ado_dt, ado_roi_neat) -> ado_bind
    View(ado_bind)

## select columns & filter rows

Functions I use really often are `select` and `filter`. The difference between them is that `select` is for columns, and `filter` is for rows.

Let us assume that there is a dataset with 6 columns, but we only need to use 2 columns.

```{r}
family <- data.frame(name = c("Amy","Bob","Connie","Dave") ,
                     age = c(4,14,6,8),
                     hobby = c("Coding","Coding","Boldering","Filming"),
                     house = c("Ravenclaw","Slytherin","Slytherin","Gryffindor"),
                     team = c("cat","dog","cat","dog"),
                     food = c("chocolate","candy","fries","fries"))
```

This is another made-up dataset recording different children in a big family. It recorded their names, ages, hobbies, Hogwarts houses, team cat or team dog, and favorite foods.

```{r}
family
```

### select

Now we only need to know their names and their age. Therefore, we can use `select` function to choose these two columns.

```{r}
family %>%
  select(c("name","age")) 
```

### filter

Now, for some reason, we want to know who is in house Slytherin. Thus, we can use `filter` to pull these people out.

```{r}
family %>%
  filter(house == "Slytherin") 
```

That's it!

If we want to see who is in house Slytherin and Ravenclaw, then we can use `%in%` to let our R Studio know that we want people with **either** of the houses.

```{r}
family %>%
  filter(house %in% c("Slytherin", "Ravenclaw"))
```

**bonus**

If we want to **only** see the names of people who are in the Slytherin house. We can combine our `select` and `filter` function together, using our useful `pipe`.

```{r}
family %>%
  select(c("name","house")) %>%
  filter(house == "Slytherin")
```

Note that we need to also put "house" in our column of selection. If you only put "name" in it, then the R Studio would not be able to find the house Slytherin on the next step.

In other words, if you only put `select("name") %>%`, instead of `select(c("name","house")) %>%`, R Studio will give you an error message saying that object 'house' not found. I know that because I just met this error message :D

## mutate

## let's draw flags!

```{r, fig.width = 3, fig.height = 2, fig.align = "center"}
library(ggplot2)
library(dplyr)

lith <- data.frame(name=c("A","B","C") ,
                   value=c(4,4,4))

lith %>%
  ggplot(aes(x = name, y = value)) +
  geom_bar(stat = "summary", width = 1, fill = c("#BE3A34","#046A38","#FFB81C")) +
  coord_flip()+
  theme_void()
```

```{r, fig.width = 4, fig.height = 2, fig.align = "center"}
latv <- data.frame(name=c("A","B","C") ,
                   value=c(4,4,4))

latv %>%
  ggplot(aes(x = name, y = value)) +
  geom_bar(stat = "identity", width = c(1.2, 0.9, 1.2), fill = c("#A4343A","#FFFFFF","#A4343A")) +
  coord_flip()+
  theme_void()
```

I am still a bit struggling with the width part. The flag looks okay but I don't think this is the correct way to do it.

Now let's try some with vertical lines.

```{r, fig.width = 3, fig.height = 2, fig.align = "center"}
ital <- data.frame(name=c("A","B","C") ,
                   value=4)

ital %>%
  ggplot(aes(x = name, y = value)) +
  geom_bar(stat = "identity", width = 1, fill = c("#008C45","#F4F9FF","#CD212A")) +
  theme_void()
```

Still struggling with the Icelandic flag. Stay tuned.

```{r, fig.width = 4, fig.height = 2, fig.align = "center"}
specie <- c("A","B" ,"C","D","E","F","G","H","I")
condition <- c("a","b","c","d","d","c","d","c","d",
               "e","a","b","c","d","c","d" ,"b","c",
               "d","e","a","b","d","c","d","a" ,"b",
               "c","d","e","a","d","c","d","e", "a" ,
               "b","c","d","e","d" ,"c","d","d","e")
value <- c(6, 0.75, 1, 0.75, 3)
data <- data.frame(specie,condition,value)
ggplot(data, aes(fill=condition, y=value, x=specie)) + 
  geom_bar(position="fill", stat="identity", width = 1)+
  scale_fill_manual(values=c("blue", "white", "red","white","blue")) +
  coord_flip() +
  theme_void()


```
