---
title: "Hello and welcome to **me, myself, and R**"
author: "by *cocoyamo*"
date: "updated: 2024-06-06"
output:
  html_document: 
    fig_caption: yes
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## introduction

**I have a toxic relationship with R Studio**

Hi, I am a student (not anymore very soon) who has been struggling with R Studio. Loving it and hating it (sometimes).

I use statistical analysis like t-tests, ANOVAs, and linear regressions often. I love to make graphs inside R Studio. Therefore I think it would be a great idea to post my journey here, mostly so that I won't have to go to my past files and copy my codes whenever I want to do a new analysis.

Sometimes I use R Studio to do funny stuff, like drawing national flags, just for fun. So you will probably see those here.

Feel free to leave comments or suggestions, I am still an infant in the fascinating world of R, and am open to learn new things!

Best, *cocoyamo*

Reykjavik, 2024

## first thing first: ``install`` and ``library``

I wish someone use this analogy when I was learning R Studio for the very first time. 

People are constantly saying "oh you need to **install** this package", and therefore I install every packages every time I am using R Studio. 

Then people will ask you to "call the package out" using a function called ``library``.

These two things inside R Studio confused me a lot in the beginning, (and I was mocked by a teaching assistant who was very inconsiderate of people who have never learned coding before), hopefully here you can find some answer. And I will not mock you. I swear. I know the struggles.

I now think of this as making a sandwich. Pick whatever sandwich you like. I will do a peanut butter and chocolate sandwich here. 

So, imagine you are going to make peanut butter and chocolate sandwich. You need ingredients. So you went to a nearby grocery store to purchase *chocolate spread*, *peanut butter*, and *toast*. (Feel free to switch to any other food you like, also please do not follow my recipe if you are allergic to peanut!)

This step (getting ingredients from a store) is called ``install``.

Then, you go back to your kitchen, pull these ingredients out from your reusable bag, this action is similar to the ``library`` function. 

Let's assume these ingredients will never run out. (What a heaven!) Then, the next time you want the peanut butter and chocolate sandwich, all you need to do is to pull out these ingredients again. **There is no need to go back to the store every time you want it, you already have it in your kitchen!**

Therefore, whenever you need to use some package you have not used before, you need to ``install`` them first, and then afterwards, the only thing you need to do is to use the ``library`` function to pull these magical stuff out of your bag. 

Okay, I hope you are still with me, and not already in the kitchen looking for your chocolate spread. 

## import file/dataset

Let's import our data!

**note: If this is your first time import data, and if your data is from an Excel file, then remember to type ``install.packages(readxl)`` on your coding space first. **

```{r echo = FALSE}
#install.packages("readxl")
```

There are of course tons of ways to import your data, but the following is what I use most often.

I will click ``Import Dataset`` on the top right corner in the ``Environment`` box. 
Then choose ``import``, chose ``From Excel`` (or ``From Text`` if I have a .csv file), then use ``Browse`` on the top right corner to pick up the file I want to import.

You can either double-click or click it once and then click the "open" at the bottom right. 

The middle part is the ``Data Preview``, you can see your data here, don't import the wrong file!(I've done that multiple times, especially when I am lazy at giving files proper names :P)

Then, you look at the bottom right corner, there is a section called ``Code Preview``.

The code can look something like this. (But not identical! Because (hopefully) we are using different file names.)

```{r}
library(readxl)
wether_math <- read_excel("example files/wether_math.xlsx")
View(wether_math)
```

Now you have seen the ``Code Preview`` section, at the end of it there is a tiny icon looking like a clipboard, you do what? CLICK IT!

**Great Job!!**

Now you have copied the code necessary to import your file, press ``Import`` at the bottom right. 

Go back to the coding section. Paste (``Ctrl + v``/``Command + v``) it on the coding section (the top left section of the interface).

(Let's hope R Studio never change their interface or else I will have to rewrite this part.)


## my happiness universe with tidyverse



## t-tests(with graph)



## ANOVAs(also with graphs)




